\documentclass[12pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{array}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\usepackage{framed}
\usepackage{listings}
\usepackage{pxfonts}
\usepackage{longtable}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage{makecell}
\pagestyle{plain}

\renewcommand{\baselinestretch}{1.2}
\renewcommand{\arraystretch}{1.3}

\lstset{%
  language=Java,
  basicstyle=\fontsize{9}{11}\selectfont\ttfamily,
  keywordstyle=\bfseries,
  breaklines=true,
  columns=fullflexible,
  frame=single,
  showstringspaces=false,
  tabsize=4,
  morekeywords = {main},
}

\begin{document}
\begin{center}
	\textbf{CS-200-1: Programming I}\\
	\textbf{Spring 2017}\\
	\textbf{Northeastern Illinois University}\\
	\textbf{Peer Evaluation Sheet}
\end{center}

\noindent\textbf{Instructions}
\begin{itemize}
	\item Each group member MUST turn in a readable .pdf or .jpg of a fully completed Peer Evaluation sheet to the individual D2L Dropbox by the specified due date/time.
	\item Each group member must complete the table and answer the questions below. \textbf{Use full sentences and proper grammar.}
	\item Students who do not fully complete and turn in the Peer Evaluation sheet will receive a grade of zero.
\end{itemize}

\vspace*{0.4cm}
\noindent Write the names of your group members in the numbered boxes. Then, assign yourself a value for each listed attribute. Finally, do the same for each of your group members and total all of the values.
\begin{center}
\textbf{Values:\hspace{0.1cm} 5 = Superior\hspace{0.1cm} 4 = Above Average\hspace{0.1cm} 3 = Average\hspace{0.1cm} 2 = Below Average\hspace{0.1cm} 1 = Weak\hspace{0.1cm} 0 = None }
\end{center} 
\noindent\begin{longtable}{| >{\centering}p{3cm} | >{\centering}p{4cm} | p{4cm} | p{4cm} |}

	\hline\rule{0pt}{4ex}
	\textbf{Attribute} & \textbf{Myself} & \textbf{1.} & \textbf{2.}\\
	\endfirsthead
		
	\hline
	\multicolumn{4}{|l|}{Continued from previous page}\\
	\hline\rule{0pt}{4ex}
	\textbf{Team Member Name} & \textbf{Myself} & \textbf{1.} & \textbf{2.}\\
	\endhead
	
	\hline
	\multicolumn{4}{|l|}{Continued on next page}\\
	\hline
	\endfoot

	\hline
	\endlastfoot
	
	\hline\rule{0pt}{3ex}
	Effective communication & & & \\[2ex]
	\hline\rule{0pt}{3ex}
	Contributed useful ideas & & & \\[2ex]
	\hline\rule{0pt}{3ex}
	Contribution to project work & & & \\[2ex]
	\hline\rule{0pt}{3ex}
	Quality of completed work  & & & \\[2ex]
	\hline\rule{0pt}{3ex}
	Worked well with all team members  & & & \\[2ex]
	\hline\rule{0pt}{3ex}
	Overall was a valuable team member  & & & \\[2ex]
\end{longtable}

\newpage
\noindent\textbf{Answer the following questions (use complete sentences and proper grammar!):}
\begin{enumerate}
	\item Give one specific example of something you learned from the team that you probably would not have learned on your own. 
	\vspace*{3.5cm}
	\item Give one specific example of something other team members learned from you that they probably would not have learned without you. 
	\vspace*{3.5cm}
	\item What are three ways you did well in functioning as a team? 
	\begin{itemize}
		\item
		\vspace*{1cm}
		\item 
		\vspace*{1cm}
		\item\vspace*{1cm}
	\end{itemize}
	\vspace*{1cm}
	\item Suggest at least one change the team could make could be made to improve its performance on the project. 
\end{enumerate}
	
\end{document}